---
format: 
  html:
    toc: true
    toc-depth: 4
---
```{r echo = FALSE, message = FALSE, warning = FALSE}

library(tidyverse)
library(xfun) # numbers_to_words function
library(lubridate)


year <- 2025

data <- read.csv(paste0("data/", year, "_annualreportdata.csv"))

  data$FirstVisit <- as_date(data$FirstVisit)
  data$FirstVisit <- paste(month(data[,"FirstVisit"], 
                           label = TRUE, abbr = FALSE), 
                           day(data[,"FirstVisit"]), 
                           sep = " ")
  data$LastVisit <- as_date(data$LastVisit)
  data$LastVisit <- paste(month(data[,"LastVisit"], 
                          label = TRUE, abbr = FALSE), 
                          day(data[,"LastVisit"]), 
                          sep = " ")

```

# Department of Defense 

## DOD Lands in Colorado 


```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# CO-BCR18-DO is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR18-DO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::


## DOD Lands in Utah 


```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9-DD is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9-DD")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9 Department of Defense lands is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9 Department of Defense lands")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9-AP is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9-AP")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9-MU is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9-MU")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9-TS is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9-TS")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9-UR is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9-UR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# UT-BCR9-UT is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "UT-BCR9-UT")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::


## DOD Lands in Wyoming 


```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This script should not need to be updated year to year!

# WY-BCR18-DO is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "WY-BCR18-DO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities (birds per square kilometer) for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of occupied plots throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of approximate survey locations, species counts, and density, occupancy, & trend estimates within {name} across all years of the project, visit the [RMADC](https://app.bcr.eco/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

